Streaming CityJSON datasets

### 2024-05-01 paper/main.tex
Proofreading 1

With \emph{cjseq}, we have converted several publicly available files, and Table~\ref{tab:datasets} shows an overview of the files stored both in CityJSON and CityJSONSeq.
The files themselves and their details are available at \url{https://github.com/cityjson/paper_cjseq/tree/main/data}.

@@

First observe that---contrary to intuition---the size of a dataset serialised as a CityJSONSeq file is around 12\% more compact than serialised as a CityJSON file, and in the case of \emph{Helsinki} it is 28\% compacter.
The main reason for this is that the indices of the vertices are low integers for each feature (because the lowest index in each feature is always ``0''), and do not increase to very large integers.
For instance, the dataset \emph{Helsinki} contains a total of more than 3 millions vertices, but its largest feature contains only but 2202 vertices.
The fact that many indices are used for representing the geometries (and for the textures) means that if several large numbers are used then the size of the file will grow; if the maximum vertex index is around 2000 for each feature then the filesize will be less than the original file.

@@

Only one dataset sees its size slightly increase by 4\% when serialised to a CityJSONSeq file: \emph{Rotterdam}.
One reason for this is that the size of the CityJSON file is rather small in the first place, and therefore the indices are not high values.
As an experiment, we have created around 125 synthetic CityJSON datasets containing buildings, and each building is represented as a simple cube randomly generated.
There are no attributes, no semantics, no textures/materials. 
Figure~\ref{fig:synthetic_compression} shows that, as the CityJSON filesize increases, the compression factor increases.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/synthetic_compression.pdf}
  \caption{Compression factor of CityJSONSeq files for different synthetic datasets containing only but simple cuboid buildings.}%
\label{fig:synthetic_compression}
\end{figure}
The smallest file contains only 526 buildings and its compression factor is -2\% (thus CityJSONSeq has a larger filesize than that of CityJSON), while the largest file has \num{3960105} buildings, and a compression factor of 18\%.

>>>>

We have converted with \emph{cjseq} several publicly available files, and Table~\ref{tab:datasets} shows an overview of the files stored both in CityJSON and CityJSONSeq.
The files themselves are available at \url{https://github.com/cityjson/paper_cjseq/tree/main/data}.

@@

First observe that---contrary to intuition---the filesize of a dataset serialised as a CityJSONSeq file is around 12\% compacter than serialised as a CityJSON file, and in the case of \emph{Helsinki} it is 28\%.
The main reason for this is that the indices of the vertices are low integers for each feature (because the lowest index in each feature is always ``0'' and is incremented by 1 until the total number of vertices), and do not increase to very large integers.
For instance, the dataset \emph{Helsinki} contains a total of more than 3 millions vertices, but its largest feature contains only but 2202 vertices.
The fact that many indices are used for representing the geometries (and for the textures) means that if several large numbers are used then the filesize will grow; if the maximum vertex index is around 2000 for each feature then the filesize will be reduced.

@@

Only one dataset sees its filesize slightly increase, by 4\%, when serialised to a CityJSONSeq file: \emph{Rotterdam}.
One reason for this is that the size of the CityJSON file is rather small in the first place, and therefore the indices are not large integers.
As an experiment, we have created around 100 synthetic CityJSON datasets containing buildings, and each building is represented as a simple cube randomly generated.
There are no attributes, no semantics, and no textures/materials. 
Figure~\ref{fig:synthetic_compression} shows that, as the CityJSON filesize increases, the compression factor increases.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/synthetic_compression.pdf}
  \caption{Compression factor of CityJSONSeq files for different synthetic datasets containing only but simple cuboid buildings.}%
\label{fig:synthetic_compression}
\end{figure}
The smallest file contains 526 buildings and its compression factor is -2\% (thus CityJSONSeq has a larger filesize than that of CityJSON), while the largest file has \num{3960105} buildings, and a compression factor of 18\%.
